Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-05 neurips-20/cvx-flats.tex
spellcheck
abstract and intro comments

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous work implicitly relied on calibration essentially \raf{Tried ``essentially''} only via property elicitation. 
For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension typically increases the computational\botodo{and sample?}\raft{I think so, but not sure -- you'd probably know better} complexity of learning.
We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.  I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.  Probably the biggest issue was in laying out the gap.  You often need to give more detail about what \emph{has} been done to say what hasn't.}

@@

% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
% the existence of consistent convex surrogates in a given dimension $d$.
% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propogated}

@@

%The proof takes its insipration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}. \jessiet{How to rephrase this?}
\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}

@@

\jessie{D $\implies$ C}
Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.

>>>>

\begin{abstract}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
While calibration has historically been used to reason about consistency, we propose indirect property elicitation as an alternative necessary condition for a surrogate loss to be consistent. 
Motivated by structured prediction and other domains where the prediction dimension of the surrogate is of central importance, we give a novel lower bound on the prediction dimension. 
Our lower bound tightens existing results in the case of discrete predictions, namely the feasible subspace dimension, showing that previous calibration-based bounds can largely be recovered purely via property elicitation.
For continuous predictions, our lower bound gives new results for variance estimation as well as the estimation of entropy and norms of the conditional distribution.
\end{abstract}

@@

Motivated by structural prediction and other problems with exponentially or infinitely large label sets, we are particularly interested in the \emph{prediction dimension} of a surrogate: the dimension $d$ of its prediction space $\reals^d$.
A natural tension arises between consistency and the prediction dimension, as consistency is always possible for a sufficiently large dimension, but a larger dimension can increase the computational and sample complexity of learning.
We are therefore interested in finding consistent convex surrogates with a low prediction dimension, such as logarithmic in the number of labels, as is desired in many structured prediction problems~\cite{ramaswamy2018consistent,yu2018lovasz,berman2018lovasz}.
%\raft{FYI Jessie: what used to be this last paragraph still didn't quite get where you want to be in terms of motivating the problem.  I'd suggest taking a careful look at the diff at some point to see what I changed and ask me if you don't see why.  Probably the biggest issue was in laying out the gap.  You often need to give more detail about what \emph{has} been done to say what hasn't.}

@@

% After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
% Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
% the existence of consistent convex surrogates in a given dimension $d$.
% This result is closely related to those provided by~\citet[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
% We illustrate our main result with several examples (\S~\raf{examples}), one of which addresses an open question posed by~\citet[Section 8]{frongillo2018elicitation} in the continuous estimation setting.
%\raft{FYI: use citet when treating citations as nouns; citep is used when the citation does not participate in the grammar, like: ``That is funny [Noah Alexander Frongillo, personal communication, 5/31/2020].''  Not sure what 'cite' does in this style...}\jessiet{Noted, and propagated}

@@

%The proof takes its inspiration from~\citet[Theorem 16]{ramaswamy2016convex}, and extracts a witness $W$ of the optimality of a surrogate prediction $u$.
%This witness $W$ takes the form of a matrix whose columns are selection of subgradients of $L$, and thus $u$ must also be optimal for any other distribution in the flat defined by the kernel of $W$.
%As we show next, the original statement of~\citet[Theorem 16]{ramaswamy2016convex}, which uses the stronger notion of calibration and thus applies only to discrete target losses, actually follows as a special case of Theorem~\ref{thm:cvx-flats}. \jessiet{How to rephrase this?}
\botodo{I suggest cutting this paragraph entirely if we keep the full proof in. We mention above that it takes inspiration from Ramaswamy.}\jessiet{agreed; cutting this paragraph}

@@

\jessie{D $\implies$ C}
Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
As $u$ is in the space over which the supremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
